Holomorphic field theories and higher algebra

### 2024-09-20 draft.tex
prophylactic protection from bad merges

\owen{To thank: Kevin Costello, Si Li, Davide Gaiotto, Ed Segal, Chris Elliott, Pavel Safronov, Kapranov, Hennion, Matt Szczesny, Richard Eager, Ingmar Saberi, Johannes Walcher, Jie Zhou, Minghao Wang, Nik Rozenblyum}

>>>>

\owen{To thank: Kevin Costello, Si Li, Davide Gaiotto, Ed Segal, Chris Elliott, Pavel Safronov, Kapranov, Hennion, Matt Szczesny, Richard Eager, Ingmar Saberi, Johannes Walcher, Jie Zhou, Minghao Wang, Nik Rozenblyum, Natalie Paquette, Nik Garner}
